Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
minor changes

where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and the observation noise is an i.i.d. Gaussian white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$. % $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.

>>>>

where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d. Gaussian white noise process . % $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.
